---
title: "Regression Models Course Project"
author: "Koji"
date: "2018/7/21"
output:
  pdf_document: default
  html_document: default
---

# Overview

Our work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

- “Is an automatic or manual transmission better for MPG”
- "Quantify the MPG difference between automatic and manual transmissions"

# Exploratory data analysis

```{r, warning=FALSE, message=FALSE}
library("ggplot2")
library("GGally")
library("gridExtra")
library("dplyr")
# Load data
data(mtcars)
```


## Compute summary statistics of data subsets:

```{r}
aggregate(mpg ~ factor(am, labels = c("AT", "MT")), mtcars, mean)
```

## Compute correlation:

```{r}
round(cor(mtcars), 2)[1, ]
```

## Fit multiple models

```{r}
fit1 <- lm(mpg ~ am, mtcars)
fit2 <- lm(mpg ~ am + wt, mtcars)
fit3 <- lm(mpg ~ am + wt + hp, mtcars)
fit4 <- lm(mpg ~ am + wt + hp + disp, mtcars)
fit5 <- lm(mpg ~ am + wt + hp + disp + cyl, mtcars)
```

```{r}
anova(fit1, fit2, fit3, fit4, fit5)
```

# Appendix

## Fig. 1
```{r, message=FALSE}
# Factorize
mtcars$am <- factor(mtcars$am, labels = c("AT", "MT"))
ggpairs(mtcars[, c(1, 9, 6, 4)], aes(color = am, alpha = .4))
```

## Fig. 2
```{r, message=FALSE}
# Residuals vs Fitted
plot1 <- ggplot(fit3, aes(.fitted, .resid)) +
        geom_point() +
        geom_hline(yintercept = 0) +
        geom_smooth(se = FALSE) +
        ggtitle("Residuals vs Fitted")
# Normal Q-Q
plot2 <- ggplot(fit3) +
        stat_qq(aes(sample = .stdresid)) +
        geom_abline() +
        ggtitle("Normal Q-Q")
# Scale-Location
plot3 <- ggplot(fit3, aes(.fitted, sqrt(abs(.stdresid)))) +
        geom_point() +
        geom_smooth(se = FALSE) +
        ggtitle("Scale-Location")
# Standardized Residuals vs Leverage
plot4 <- ggplot(fit3, aes(.hat, .stdresid)) +
        geom_point(aes(size = .cooksd)) +
        geom_smooth(se = FALSE) +
        ggtitle("Residuals vs Leverage")

grid.arrange(plot1, plot2, plot3, plot4, ncol = 2)
```

